---
title: "Week 06 Coding challenge"
name: [ ]
output: html_notebook
---

Coding challenge for this week focuses on `data wrangling` and applying `multilevel modeling`. Please refer to the coding demonstration as a guide. 
You will be using `county` information from Texas for this assignment. 

>Libraries needed for this demonstration

```{r load libraries}
library(tidyverse)
library(tidymodels)
library(naniar)#replace specific value as NA
library(lme4) #for MLM; install it first if needed
library(lattice) #for dotplot; install it first if needed
library(afex) #for p-value in LME; install it first if needed.
library(splines)
library(gam)
library(mgcv)
```



#load data set "LHS_TEXAS.csv"
```{r include=FALSE}
# write your code here

```

# How many observations? 
**answer** 
>


# How many variables? 
**answer**
>


#we will focus on covid-19 related issues; refer to the codebook. 


## create a new varaible called `county_regions` and group counties into 12 regions. Use `texas county regions.xlsx` file for your reference. Please note that these type of information are provided for this week's coding challenge; however, for your final project, you will have to search and apply outside information on your own. 


```{r}
## your code goes here


```
# use `table ()` function to see frequency for each county_regions. Which county_region has the biggest sample? State the name of county_region and its sample size. 
**answer**
>>


# which county_region(s) has the smallest sample? State the name of county_region and its sample size:
**answer**
>>



#since some county_regions have only 1 participant, we need to find a way to combine some regions into more general regions: 

Combine `Rio Grande`, `West`, `southern` and name it as `southwest_region` (75)
Combine `Alamo`, `Capital`, `Central` and name it as `capital_region` (121)
Combine `gulf coast`, `southeast` and name it as `east_region` (89)
Combine `metroplex`, `upper east`, `northwest`, `high plains` and name it as `north_region` (99)

```{r}
## your code goes here

```

# use `table()` function to describe the four regions
**answer**
>>



#data wrangling - make sure you reverse codes where needed. 
# create the following variables: 
- `covid_awareness` = refer to the codebook pg 18; use mean score
- `ptsd_mean` = refer to the codebook; use mean score
- `distress` = refer to the codebook; use sum score
- remove `5` on 9 items listed for covid negative impact
- score mean `covid_neg_impact` variable using the 9-items listed, but remove individuals that have more than 50% of the missing responses; 
- convert the `covid_neg_impact` mean score to a sum score

```{r}
## your code goes here


```


#compute mean, SD, and number of missing of the `covid_neg_impact` for the four general regions:

```{r}

```

#describe your result:
**answer**
>>


#compute mean, SD, and number of missing of the `covid_awareness` for the four general regions:

```{r}


```



#Plot density plot using `covid_neg_impact` by the four general regions:

```{r}


```

#describe your observation:
**answer**
>>



# Scale `covid_awareness` and `covid_neg_impact` so they have the same mean and units

```{r}


```


#Fit linear model and use `ggplot` to plot the predicted line by regions

#DV: covid_neg_impact; IV: covid_awareness

```{r}

```


#fit linear model with splines at (-1,0,1) and use `ggplot to plot the predicted line by regions; for your ggplot, use `geom_smooth (method="gam")` or geom_smooth (method="loess")

```{r}

```


# Compare the plots and explain how they are different? 
**answer**
>>





## Now use `lmer` with random intercept; use the four county regions as your group variable;
#use spline knot points at -1, 0, 1, then plot predicted line by regions; use method="gam" for your geom_smooth() function.

```{r}



```

#describe your plot: 
**answer**
>>




## Now use `lmer` model with random intercept and slope; use the county regions as your group variable and use your IV as slope. Use spline knot points at -1, 0, 1, then plot prediced line by regions; use method="gam" for  your geom_smooth() function.

```{r}


```

#describe your plot:
**asnwer**
>>








